\iffalse
This file is protected by Copyright. Please refer to the COPYRIGHT file
distributed with this source distribution.

This file is part of OpenCPI <http://www.opencpi.org>

OpenCPI is free software: you can redistribute it and/or modify it under the
terms of the GNU Lesser General Public License as published by the Free Software
Foundation, either version 3 of the License, or (at your option) any later
version.

OpenCPI is distributed in the hope that it will be useful, but WITHOUT ANY
WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A
PARTICULAR PURPOSE. See the GNU Lesser General Public License for more details.

You should have received a copy of the GNU Lesser General Public License along
with this program. If not, see <http://www.gnu.org/licenses/>.
\fi

%----------------------------------------------------------------------------------------
% Required document specific properties
%----------------------------------------------------------------------------------------
\def\comp{advanced\_{}pattern}
\edef\ecomp{advanced_pattern}
\def\Comp{Advanced Pattern}
\def\docTitle{\Comp{} Component Data Sheet}
\def\snippetpath{../../../../../../doc/av/tex/snippets}
%----------------------------------------------------------------------------------------
% Global latex header (this must be after document specific properties)
%----------------------------------------------------------------------------------------
\input{\snippetpath/LaTeX_Header}
%----------------------------------------------------------------------------------------

\begin{document}
\maketitle
\thispagestyle{empty}
\newpage

\def\name{\comp}
\def\workertype{Application}
\def\version{\ocpiversion}
\def\releasedate{4/2019}
\def\componentlibrary{ocpi.assets.util\_{}comps}
\def\workers{\comp{}.rcc}
\def\testedplatforms{CentOS7, xilinx13\_{}3 (limited)}
\input{\snippetpath/component_summary_table}

\section*{Functionality}
\begin{flushleft}
	The Advanced Pattern Component provides predefined data to assist in the testing of other Components.\par\medskip
	The data can be arranged in messages of up to 2048 bytes at a time with each block having a specific opcode. By default, 32 of these messages are available, but that configuration is exposed as a build-time parameter with a default configuration building additional Workers allowing for 64, 128, and 256 messages.
\end{flushleft}
\begin{center}
\framebox{\parbox{0.8\linewidth}{\centering This Component provides \textit{minimal} error checking and is \textbf{not recommended for production use}, but is only intended for prototyping and testing of other Components.}}
\end{center}

\section*{Block Diagrams}
\subsection*{Top level}
\begin{center}
	\begin{tikzpicture}[% List of styles applied to all, to override specify on a case-by-case
			every node/.style={
				align=center,  		% use this so that the "\\" for line break works
				minimum size=2cm	% creates space above and below text in rectangle
			},
			every edge/.style={draw,thick}
		]
		\node[rectangle,ultra thick,draw=black,fill=blue](R2){\Comp};
		\node[rectangle,draw=white,fill=white](R4)[right= of R2]{``out'' \\ Data defined in properties};
		\node[rectangle,draw=white,fill=white](R5)[above= of R2]{See property table};
		\path[->]
		(R2)edge []	node [] {} (R4)
		(R2)edge []	node [] {} (R5)
		(R5)edge []	node [] {} (R2)
		;
	\end{tikzpicture}
\end{center}

\section*{Source Dependencies}
\subsection*{\comp.rcc}
\begin{itemize}
	\item $<$assets$>$/components/util\_comps/advanced\_pattern.rcc/advanced\_pattern.cc
\end{itemize}

\begin{landscape}
	\newcounter{fnreadable}
	\section*{Component Spec Properties}
	\begin{scriptsize}
		\begin{minipage}{\textwidth}
			\renewcommand*\footnoterule{} % Remove separator line from footnote
			\renewcommand{\thempfootnote}{\arabic{mpfootnote}} % Use Arabic numbers (or can't reuse)
			\begin{tabular}{|p{3cm}|p{1.5cm}|c|c|c|c|c|p{7cm}|}
				\hline
				\rowcolor{blue}
				Name &
				Type &
				SequenceLength &
				ArrayDimensions &
				Accessibility &
				Valid Range &
				Default &
				Usage \\
				\hline
				\verb+maxPatternLength+ &
				ULong &
				- &
				- &
				Parameter &
				Standard &
				32 &
				Maximum ``\textbf{Pattern}'' sequence length to allow \footnote{Each \textbf{Pattern} entry requires about 2K of RAM.} \\
				\hline
				\verb+Pattern+ &
				Struct &
				\verb+maxPatternLength+ &
				- &
				Initial, Readable\footnote{``Readable'' is deprecated and superfluous here. It will be removed in a future release.}\setcounter{fnreadable}{\thempfootnote} &
				- &
				- &
				Message to send \\
				\hline
				\verb+Pattern.Opcode+ &
				UChar &
				- &
				- &
				'' &
				Standard &
				0 &
				Opcode metadata to send with this message's data \\
				\hline
				\verb+Pattern.Bytes+ &
				UChar &
				2048 &
				- &
				'' &
				Standard &
				0 &
				Data to send \\
				\hline
				\verb+LoopCount+ &
				ULongLong &
				- &
				- &
				Initial, Readable\footnotemark[\thefnreadable] &
				Standard &
				1 &
				How many times to repeat the ``\textbf{Pattern}'' sequence\footnote{0 will continue as long as Worker is running.} \\
				\hline
				\verb+ZLM+ &
				UShort &
				- &
				- &
				Initial, Readable\footnotemark[\thefnreadable] &
				0 \ldots 256 &
				0 &
				Opcode for a \textbf{Z}ero \textbf{L}ength \textbf{M}essage with when finished.\footnote{Default is opcode 0; set to invalid opcode 256 if this feature is \textit{not} desired.} \\
				\hline
				\verb+current+ &
				Struct &
				- &
				- &
				Volatile &
				- &
				- &
				Current statistics for each opcode \\
				\hline
				\verb+current.Total+ &
				Struct &
				- &
				- &
				'' &
				- &
				- &
				Statistics across \textit{all} opcodes \\
				\hline
				\verb+current.Total.bytes+ &
				ULongLong &
				- &
				- &
				'' &
				Standard &
				- &
				Number of bytes received \\
				\hline
				\verb+current.Total.messages+ &
				ULongLong &
				- &
				- &
				'' &
				Standard &
				- &
				Number of messages received \\
				\hline
				\verb+current.Opcode+ &
				Struct &
				- &
				256 &
				'' &
				- &
				- &
				Statistics for \textit{each} opcode \\
				\hline
				\verb+current.Opcode.*+ &
				Various &
				- &
				- &
				'' &
				- &
				Various &
				Various\footnote{Internal structure equivalent to \texttt{current.Total} and not explicitly shown.} \\
				\hline
			\end{tabular}
		\end{minipage}
	\end{scriptsize}
	\section*{Worker Properties}
	There are no implementation-specific properties for this component.

	\section*{Component Ports}
	\begin{scriptsize}
		\begin{tabular}{|M{2cm}|M{1.5cm}|M{4cm}|c|c|M{9cm}|}
			\hline
			\rowcolor{blue}
			Name & Producer & Protocol & Optional & Advanced            & Usage                      \\
			\hline
			out  & true     & -        & -        & numberofopcodes=256 & Data defined in properties \\
			\hline
		\end{tabular}
	\end{scriptsize}

	\section*{Worker Interfaces}
	There are no implementation-specific interfaces for this component.

\end{landscape}
\iffalse
\section*{Performance and Resource Utilization}
\subsubsection*{\comp.rcc}
\begin{scriptsize}
	\begin{tabular}{|c|c|c|}
		\hline
		\rowcolor{blue}
		Processor Type                                & Processor Frequency & Run Function Time \\
		\hline
		linux-c6-x86\_64 Intel(R) Xeon(R) CPU E5-1607 & 3.00 GHz            & TBD               \\
		\hline
		linux-c7-x86\_64 Intel(R) Core(TM) i7-3630QM  & 2.40 GHz            & TBD               \\
		\hline
		linux-x13\_3-arm ARMv7 Processor rev 0 (v7l)  & 666 MHz             & TBD               \\
		\hline
	\end{tabular}
\end{scriptsize}
\fi
\section*{Test and Verification}
The {\comp} worker is tested using five cases. All cases are verified using the md5 hashes of different        properties and or the output file against the expected md5 hashes. A sixth case, {\path{test_05}}, is present but not tested due to sending a ZLM with opcode 1. The {\path{file_write}} component cannot currently stop on ZLM with opcodes other than 0.\\

{\path{case 00}} runs default values and sends a single ZLM with opcode 0. The output file and the contents of the \verb+current+ property are compared to the expected.\\

{\path{case 01}} also runs default values but does not send a ZLM and instead times out after 10 seconds. The \verb+current+ property is compared to the expected.\\

{\path{case 02}} generates the \verb+Pattern+ property {(\path{generate.py} 2)} and sends three bytes every tenth opcode. The \verb+maxPatternLength+ property is explicitly set to be 256. The output file, contents of the \verb+current+ property, and, contents of the \verb+maxPatternLength+ property are compared to the expected.\\

{\path{case 03}} generates the \verb+Pattern+ property {(\path{generate.py} 3)} and sends three bytes every tenth opcode, 50 times. There is no ZLM sent and the test case times out after 10 seconds. The \verb+maxPatternLength+ property is set to 64. For clarity, an {\path{Output_03.out}} file is created to see from where the output hashes are gotten. The output file, contents of the \verb+current+ property, and, contents of the \verb+maxPatternLength+ property are compared to the expected.\\

{\path{case 04}} generates 2048 bytes of data for the \verb+Pattern+ property {(\path{generate.py} 4)} and sends 3 bytes with opcode 0 for 10 seconds. The contents of the \verb+maxPatternLength+ property, and the end cut of the \verb+current+ property are compared to the expected. 
\end{document}
